---
title: "Reproducibility report"
output: html_document
date: "2023-07-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=F}
setwd("//file.phhp.ufl.edu/data/home/ark007/Documents/GitHub/Bayesian_forest_clustering")
```

## Figure 1 is an illustrative plot that can be generated using "clusterSim" R package, and does not require fitting of the Bayesian spanning forest model.

```{r, echo=T}
library(clusterSim)
```

## Figure 2 can be generated using "compare_eigenvectors.r".

```{r, echo=T}
source("compare_eigenvectors.r")
```

## Figure 3 can be generated using "uq_near_manifold.r".

```{r, echo=T}
source("Uncertainty_Quantification\\uq_near_manifold.r")
```

## Figure 4 and 5 can be generated using "fmri_application/multiview_fmri_application.Rmd".

Run the Forest model
```{r, echo=T}
source("fMRI_application\\fMRI_analysis.r")
```

Produce plots and illustrations of the above produced results
```{r, echo=T}
source("fMRI_application\\fMRI_analysis_results.r")
```
## Figure S.1, S.2 and Table S.1 can be generated using "high_dim_application/uq_high_dimesion_clustering.r".

```{r, echo=T}
source("High_dimensional_application/uq_high_dimesion_clustering.r")
```

## Figure S.3 can be generated using "covariate_dependent_clustering/penguins.Rmd".

```{r, echo=T}
source("covariate_dependent_clustering/penguins.r")
```

## Figure S.4 and S.5 can be generated using "uq_mixture_model_data_t_dist.r".

```{r, echo=T}
source("Uncertainty_Quantification/uq_mixture_model_data_t_dist.r")
```

## Figure S.6 can be generated using "uq_near_manifold.r".

```{r, echo=T}
source("Uncertainty_Quantification/uq_near_manifold.r")
```

## Figure S.7, S.8, S.9 can be generated using "simulations/imbalanced_vs_clusteringErr.Rmd", "simulations/num_clusters_vs_clusteringErr.Rmd", and "simulations/loosely_connected_graphs_vs_clusteringErr.Rmd". For the convenience of review, the repeated experiment results are stored in the "RDa" binary files.

```{r, echo=T}
source("Simulation/imbalanced_vs_clusteringErr.r")
source("Simulation/num_clusters_vs_clusteringErr.r")
source("Simulation/loosely_connected_graphs_vs_clusteringErr.r")

```

## Figure S.10, S.11, S.12 can be generated using "simulations/mixing_diagnostics_multiple_initialization.Rmd".

```{r, echo=T}
source("Simulation/mixing_diagnostics_multiple_initialization.r")
```

## Figure S.13 can be generated using "multiview_fmri_application/multiview_fmri_application.Rmd".

```{r, echo=T}

```

## Figure S.14 can be generated using "uq_mixture_model_data_t_dist.r".

```{r, echo=T}
source("Uncertainty_Quantification/uq_mixture_model_data_t_dist.r")
```

## Figure S.15 can be generated using "compare_eigenvectors.r".

```{r, echo=T}
source("compare_eigenvectors.r")
```
